### 2025-01-05 sections/4-results.tex
made all tables larger

\begin{table*}[h]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Queries per second (QPS) and Recall vs naive linear search on the Fashion-Mnist dataset.
    A recall value of $1.000*$ denotes imperfect recall that rounds to 1.000.}
    \label{tab:results:qps-and-recall-fmn}
    \vskip 0.15in
    \begin{center}
            \begin{tabular}{|l|p{1.55cm}|p{1.0cm}|p{1.6cm}|p{1.0cm}|p{1.6cm}|p{1.1cm}|p{1.6cm}|p{1.0cm}|}
                \hline
                \multirow{2}{*}{\textbf{Mult.}} & \multicolumn{2}{c|}{\textbf{HNSW}} & \multicolumn{2}{c|}{\textbf{ANNOY}} & \multicolumn{2}{c|}{\textbf{FAISS-IVF}}  & \multicolumn{2}{c|}{\textbf{CAKES}} \\\cline{2-9}
                & QPS & Recall & QPS & Recall & QPS & Recall & QPS & Recall \\
                \cline{1-9}
                \hline
                1   & \num{1.33e4} & 0.954  & \num{2.19e3} & 0.950  & \num{2.01e3} & 1.000* & \num{3.46e3} & 1.000  \\\cline{1-9}
                2   & \num{1.38e4} & 0.803  & \num{2.12e3} & 0.927  & \num{9.39e2} & 1.000* & \num{3.68e3} & 1.000  \\\cline{1-9}
                4   & \num{1.66e4} & 0.681  & \num{2.04e3} & 0.898  & \num{4.61e2} & 0.997  & \num{3.44e3} & 1.000  \\\cline{1-9}
                8   & \num{1.68e4} & 0.525  & \num{1.93e3} & 0.857  & \num{2.26e2} & 0.995  & \num{3.30e3} & 1.000  \\\cline{1-9}
                16  & \num{1.87e4} & 0.494  & \num{1.84e3} & 0.862  & \num{1.17e2} & 0.991  & \num{3.34e3} & 1.000  \\\cline{1-9}
                32  & \num{1.56e4} & 0.542  & \num{1.85e3} & 0.775  & \num{5.91e1} & 0.985  & \num{2.96e3} & 1.000  \\\cline{1-9}
                64  & \num{1.50e4} & 0.378  & \num{1.78e3} & 0.677  & \num{2.61e1} & 0.968  & \num{3.25e3} & 1.000  \\\cline{1-9}
                128 & \num{1.49e4} & 0.357  & \num{1.66e3} & 0.538  & \num{1.33e1} & 0.964  & \num{2.96e3} & 1.000  \\\cline{1-9}
                256 & --           & --     & \num{1.60e3} & 0.592  & \num{6.65e0} & 0.962  & \num{2.79e3} & 1.000  \\\cline{1-9}
                512 & --           & --     & \num{1.83e3} & 0.581  & \num{3.56e0} & 0.949 & \num{2.84e3} & 1.000 \\
                \hline
            \end{tabular}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[h]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Queries per second (QPS) and Recall vs naive linear search on the Glove-25 dataset.
    A recall value of $1.000*$ denotes imperfect recall that rounds to 1.000.}
    \label{tab:results:qps-and-recall-glove}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{tabular}{|c|l|p{1.4cm}|p{1.0cm}|p{1.4cm}|p{1.0cm}|p{1.4cm}|p{1.0cm}|p{1.4cm}|p{1.0cm}|}
                \hline
                & \multirow{2}{*}{\textbf{Mult.}} & \multicolumn{2}{|c}{\textbf{hnsw}} & \multicolumn{2}{|c}{\textbf{annoy}} & \multicolumn{2}{|c}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{cakes}} \\\cline{3-10}
                & & QPS & Recall & QPS & Recall & QPS & Recall & QPS & Recall \\
                \cline{2-10}

                \hline
                \multirow{9}{*}{\rotatebox[origin=c]{90}{\textbf{Glove-25}}}
                & 1   & \num{2.28e4} & 0.801 & \num{2.83e3} & 0.835 & \num{2.38e3} & 1.000* & \num{1.54e3} & 1.000* \\\cline{2-10}
                & 2   & \num{2.38e4} & 0.607 & \num{2.70e3} & 0.832 & \num{1.19e3} & 1.000* & \num{1.49e3} & 1.000* \\\cline{2-10}
                & 4   & \num{2.50e4} & 0.443 & \num{2.61e3} & 0.839 & \num{6.19e2} & 1.000* & \num{1.28e3} & 1.000* \\\cline{2-10}
                & 8   & \num{2.78e4} & 0.294 & \num{2.51e3} & 0.834 & \num{3.03e2} & 1.000* & \num{1.30e3} & 1.000* \\\cline{2-10}
                & 16  & \num{3.11e4} & 0.213 & \num{2.23e3} & 0.885 & \num{1.51e2} & 1.000* & \num{1.14e3} & 1.000* \\\cline{2-10}
                & 32  & \num{3.24e4} & 0.178 & \num{2.01e3} & 0.764 & \num{7.40e1} & 0.999  & \num{1.05e3} & 1.000* \\\cline{2-10}
                & 64  & --           & --    & \num{1.99e3} & 0.631 & \num{3.77e1} & 0.997  & \num{1.07e3} & 1.000* \\\cline{2-10}
                & 128 & --           & --    & --           & --    & \num{1.90e1} & 0.998  & \num{8.92e2} & 1.000* \\\cline{2-10}
                & 256 & --           & --    & --           & --    & \num{9.47e0} & 0.998  & \num{8.91e2} & 1.000* \\
                \hline

            \end{tabular}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[h]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Queries per second (QPS) and Recall vs naive linear search on the Sift dataset.
    A recall value of $1.000*$ denotes imperfect recall that rounds to 1.000.}
    \label{tab:results:qps-and-recall-sift}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{tabular}{|c|l|p{1.4cm}|p{1.0cm}|p{1.4cm}|p{1.0cm}|p{1.4cm}|p{1.0cm}|p{1.4cm}|p{1.0cm}|}
                \hline
                & \multirow{2}{*}{\textbf{Mult.}} & \multicolumn{2}{|c}{\textbf{hnsw}} & \multicolumn{2}{|c}{\textbf{annoy}} & \multicolumn{2}{|c}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{cakes}} \\\cline{3-10}
                & & QPS & Recall & QPS & Recall & QPS & Recall & QPS & Recall \\
                \cline{2-10}

                \hline
                \multirow{8}{*}{\rotatebox[origin=c]{90}{\textbf{Sift}}}
                & 1   & \num{1.93e4} & 0.782 & \num{3.98e3} & 0.686 & \num{6.98e2} & 1.000* & \num{6.20e2} & 1.000 \\\cline{2-10}
                & 2   & \num{2.03e4} & 0.552 & \num{3.80e3} & 0.614 & \num{3.30e2} & 1.000* & \num{2.95e2} & 1.000 \\\cline{2-10}
                & 4   & \num{2.18e4} & 0.394 & \num{3.69e3} & 0.637 & \num{1.65e2} & 1.000* & \num{1.76e2} & 1.000 \\\cline{2-10}
                & 8   & \num{2.48e4} & 0.298 & \num{3.58e3} & 0.710 & \num{7.72e1} & 1.000* & \num{1.27e2} & 1.000 \\\cline{2-10}
                & 16  & \num{2.68e4} & 0.210 & \num{3.50e3} & 0.690 & \num{3.98e1} & 1.000* & \num{1.47e2} & 1.000 \\\cline{2-10}
                & 32  & \num{2.75e4} & 0.193 & \num{3.44e3} & 0.639 & \num{2.09e1} & 0.999  & \num{1.24e2} & 1.000 \\\cline{2-10}
                & 64  & --           & --    & \num{3.39e3} & 0.678 & \num{8.87e0} & 0.997  & \num{1.34e2} & 1.000 \\\cline{2-10}
                & 128 & --           & --    & \num{3.36e3} & 0.643 & \num{4.78e0} & 0.993  & \num{1.31e2} & 1.000 \\
                \hline

            \end{tabular}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[h]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Queries per second (QPS) and Recall vs naive linear search on the Random dataset.
    A recall value of $1.000*$ denotes imperfect recall that rounds to 1.000.}
    \label{tab:results:qps-and-recall-random}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{tabular}{|c|l|p{1.4cm}|p{1.0cm}|p{1.4cm}|p{1.0cm}|p{1.4cm}|p{1.0cm}|p{1.4cm}|p{1.0cm}|}
                \hline
                & \multirow{2}{*}{\textbf{Mult.}} & \multicolumn{2}{|c}{\textbf{hnsw}} & \multicolumn{2}{|c}{\textbf{annoy}} & \multicolumn{2}{|c}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{cakes}} \\\cline{3-10}
                & & QPS & Recall & QPS & Recall & QPS & Recall & QPS & Recall \\
                \cline{2-10}

                \hline
                \multirow{6}{*}{\rotatebox[origin=c]{90}{\textbf{Random}}}
                & 1  & \num{1.17e4} & 0.060 & \num{4.28e3} & 0.028 & \num{7.342} & 1.000* & \num{5.54e2} & 1.000 \\\cline{2-10}
                & 2  & \num{1.01e4} & 0.048 & \num{4.04e3} & 0.021 & \num{3.582} & 1.000* & \num{2.69e2} & 1.000 \\\cline{2-10}
                & 4  & \num{9.12e3} & 0.031 & \num{3.64e3} & 0.014 & \num{1.902} & 1.000* & \num{1.37e2} & 1.000 \\\cline{2-10}
                & 8  & \num{8.35e3} & 0.022 & \num{3.37e3} & 0.013 & \num{8.841} & 1.000* & \num{5.69e1} & 1.000 \\\cline{2-10}
                & 16 & \num{8.25e3} & 0.008 & \num{3.17e3} & 0.006 & \num{4.361} & 1.000* & \num{2.61e1} & 1.000 \\\cline{2-10}
                & 32 & --           & --    & \num{3.01e3} & 0.007 & \num{1.721} & 1.000* & \num{1.35e1} & 1.000 \\
                \hline
            \end{tabular}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

>>>>

\begin{table*}
    \caption{Queries per second (QPS) and Recall vs naive linear search on the Fashion-Mnist dataset.
    A recall value of $1.000*$ denotes imperfect recall that rounds to 1.000.}
    \label{tab:results:qps-and-recall-fmn}
    \begin{center}
        \begin{tabular}{|l|p{1.55cm}|p{1.1cm}|p{1.55cm}|p{1.1cm}|p{1.55cm}|p{1.1cm}|p{1.55cm}|p{1.1cm}|}
            \hline
            \multirow{2}{*}{\textbf{Mult.}} & \multicolumn{2}{c|}{\textbf{HNSW}} & \multicolumn{2}{c|}{\textbf{ANNOY}} & \multicolumn{2}{c|}{\textbf{FAISS-IVF}}  & \multicolumn{2}{c|}{\textbf{CAKES}} \\\cline{2-9}
            & QPS & Recall & QPS & Recall & QPS & Recall & QPS & Recall \\
            \cline{1-9}
            \hline
            1   & \num{1.33e4} & 0.954  & \num{2.19e3} & 0.950  & \num{2.01e3} & 1.000* & \num{3.46e3} & 1.000  \\\cline{1-9}
            2   & \num{1.38e4} & 0.803  & \num{2.12e3} & 0.927  & \num{9.39e2} & 1.000* & \num{3.68e3} & 1.000  \\\cline{1-9}
            4   & \num{1.66e4} & 0.681  & \num{2.04e3} & 0.898  & \num{4.61e2} & 0.997  & \num{3.44e3} & 1.000  \\\cline{1-9}
            8   & \num{1.68e4} & 0.525  & \num{1.93e3} & 0.857  & \num{2.26e2} & 0.995  & \num{3.30e3} & 1.000  \\\cline{1-9}
            16  & \num{1.87e4} & 0.494  & \num{1.84e3} & 0.862  & \num{1.17e2} & 0.991  & \num{3.34e3} & 1.000  \\\cline{1-9}
            32  & \num{1.56e4} & 0.542  & \num{1.85e3} & 0.775  & \num{5.91e1} & 0.985  & \num{2.96e3} & 1.000  \\\cline{1-9}
            64  & \num{1.50e4} & 0.378  & \num{1.78e3} & 0.677  & \num{2.61e1} & 0.968  & \num{3.25e3} & 1.000  \\\cline{1-9}
            128 & \num{1.49e4} & 0.357  & \num{1.66e3} & 0.538  & \num{1.33e1} & 0.964  & \num{2.96e3} & 1.000  \\\cline{1-9}
            256 & --           & --     & \num{1.60e3} & 0.592  & \num{6.65e0} & 0.962  & \num{2.79e3} & 1.000  \\\cline{1-9}
            512 & --           & --     & \num{1.83e3} & 0.581  & \num{3.56e0} & 0.949 & \num{2.84e3} & 1.000 \\
            \hline
        \end{tabular}
    \end{center}
    \vskip -0.2in
\end{table*}

\begin{table*}
    \caption{Queries per second (QPS) and Recall vs naive linear search on the Glove-25 dataset.
    A recall value of $1.000*$ denotes imperfect recall that rounds to 1.000.}
    \label{tab:results:qps-and-recall-glove}
    \begin{center}
        \begin{tabular}{|l|p{1.55cm}|p{1.1cm}|p{1.55cm}|p{1.1cm}|p{1.55cm}|p{1.1cm}|p{1.55cm}|p{1.1cm}|}
            \hline
            \multirow{2}{*}{\textbf{Mult.}} & \multicolumn{2}{c|}{\textbf{HNSW}} & \multicolumn{2}{c|}{\textbf{ANNOY}} & \multicolumn{2}{c|}{\textbf{FAISS-IVF}}  & \multicolumn{2}{c|}{\textbf{CAKES}} \\\cline{2-9}
            & QPS & Recall & QPS & Recall & QPS & Recall & QPS & Recall \\
            \cline{1-9}
            \hline
            1   & \num{2.28e4} & 0.801 & \num{2.83e3} & 0.835 & \num{2.38e3} & 1.000* & \num{1.54e3} & 1.000* \\\cline{1-9}
            2   & \num{2.38e4} & 0.607 & \num{2.70e3} & 0.832 & \num{1.19e3} & 1.000* & \num{1.49e3} & 1.000* \\\cline{1-9}
            4   & \num{2.50e4} & 0.443 & \num{2.61e3} & 0.839 & \num{6.19e2} & 1.000* & \num{1.28e3} & 1.000* \\\cline{1-9}
            8   & \num{2.78e4} & 0.294 & \num{2.51e3} & 0.834 & \num{3.03e2} & 1.000* & \num{1.30e3} & 1.000* \\\cline{1-9}
            16  & \num{3.11e4} & 0.213 & \num{2.23e3} & 0.885 & \num{1.51e2} & 1.000* & \num{1.14e3} & 1.000* \\\cline{1-9}
            32  & \num{3.24e4} & 0.178 & \num{2.01e3} & 0.764 & \num{7.40e1} & 0.999  & \num{1.05e3} & 1.000* \\\cline{1-9}
            64  & --           & --    & \num{1.99e3} & 0.631 & \num{3.77e1} & 0.997  & \num{1.07e3} & 1.000* \\\cline{1-9}
            128 & --           & --    & --           & --    & \num{1.90e1} & 0.998  & \num{8.92e2} & 1.000* \\\cline{1-9}
            256 & --           & --    & --           & --    & \num{9.47e0} & 0.998  & \num{8.91e2} & 1.000* \\
            \hline
        \end{tabular}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}
    \caption{Queries per second (QPS) and Recall vs naive linear search on the Sift dataset.
    A recall value of $1.000*$ denotes imperfect recall that rounds to 1.000.}
    \label{tab:results:qps-and-recall-sift}
    \begin{center}
        \begin{tabular}{|l|p{1.55cm}|p{1.1cm}|p{1.55cm}|p{1.1cm}|p{1.55cm}|p{1.1cm}|p{1.55cm}|p{1.1cm}|}
            \hline
            \multirow{2}{*}{\textbf{Mult.}} & \multicolumn{2}{c|}{\textbf{HNSW}} & \multicolumn{2}{c|}{\textbf{ANNOY}} & \multicolumn{2}{c|}{\textbf{FAISS-IVF}}  & \multicolumn{2}{c|}{\textbf{CAKES}} \\\cline{2-9}
            & QPS & Recall & QPS & Recall & QPS & Recall & QPS & Recall \\
            \cline{1-9}
            \hline
            1   & \num{1.93e4} & 0.782 & \num{3.98e3} & 0.686 & \num{6.98e2} & 1.000* & \num{6.20e2} & 1.000 \\\cline{1-9}
            2   & \num{2.03e4} & 0.552 & \num{3.80e3} & 0.614 & \num{3.30e2} & 1.000* & \num{2.95e2} & 1.000 \\\cline{1-9}
            4   & \num{2.18e4} & 0.394 & \num{3.69e3} & 0.637 & \num{1.65e2} & 1.000* & \num{1.76e2} & 1.000 \\\cline{1-9}
            8   & \num{2.48e4} & 0.298 & \num{3.58e3} & 0.710 & \num{7.72e1} & 1.000* & \num{1.27e2} & 1.000 \\\cline{1-9}
            16  & \num{2.68e4} & 0.210 & \num{3.50e3} & 0.690 & \num{3.98e1} & 1.000* & \num{1.47e2} & 1.000 \\\cline{1-9}
            32  & \num{2.75e4} & 0.193 & \num{3.44e3} & 0.639 & \num{2.09e1} & 0.999  & \num{1.24e2} & 1.000 \\\cline{1-9}
            64  & --           & --    & \num{3.39e3} & 0.678 & \num{8.87e0} & 0.997  & \num{1.34e2} & 1.000 \\\cline{1-9}
            128 & --           & --    & \num{3.36e3} & 0.643 & \num{4.78e0} & 0.993  & \num{1.31e2} & 1.000 \\
            \hline
        \end{tabular}
    \end{center}
    \vskip -0.2in
\end{table*}

\begin{table*}
    \caption{Queries per second (QPS) and Recall vs naive linear search on the Random dataset.
    A recall value of $1.000*$ denotes imperfect recall that rounds to 1.000.}
    \label{tab:results:qps-and-recall-random}
    \begin{center}
        \begin{tabular}{|l|p{1.55cm}|p{1.1cm}|p{1.55cm}|p{1.1cm}|p{1.55cm}|p{1.1cm}|p{1.55cm}|p{1.1cm}|}
            \hline
            \multirow{2}{*}{\textbf{Mult.}} & \multicolumn{2}{c|}{\textbf{HNSW}} & \multicolumn{2}{c|}{\textbf{ANNOY}} & \multicolumn{2}{c|}{\textbf{FAISS-IVF}}  & \multicolumn{2}{c|}{\textbf{CAKES}} \\\cline{2-9}
            & QPS & Recall & QPS & Recall & QPS & Recall & QPS & Recall \\
            \cline{1-9}
            \hline
            1  & \num{1.17e4} & 0.060 & \num{4.28e3} & 0.028 & \num{7.342} & 1.000* & \num{5.54e2} & 1.000 \\\cline{1-9}
            2  & \num{1.01e4} & 0.048 & \num{4.04e3} & 0.021 & \num{3.582} & 1.000* & \num{2.69e2} & 1.000 \\\cline{1-9}
            4  & \num{9.12e3} & 0.031 & \num{3.64e3} & 0.014 & \num{1.902} & 1.000* & \num{1.37e2} & 1.000 \\\cline{1-9}
            8  & \num{8.35e3} & 0.022 & \num{3.37e3} & 0.013 & \num{8.841} & 1.000* & \num{5.69e1} & 1.000 \\\cline{1-9}
            16 & \num{8.25e3} & 0.008 & \num{3.17e3} & 0.006 & \num{4.361} & 1.000* & \num{2.61e1} & 1.000 \\\cline{1-9}
            32 & --           & --    & \num{3.01e3} & 0.007 & \num{1.721} & 1.000* & \num{1.35e1} & 1.000 \\
            \hline
        \end{tabular}
    \end{center}
    \vskip -0.1in
\end{table*}
